%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{paralist}

\name{Yang Pan} % Your name
\address{147 N Craig St. Apt 37 \\ Pittsburgh, PA 15213} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(312)~$\cdot$~721~$\cdot$~2965 \\ pystone9205@gmail.com \\
ysite.me} % Your phone number and email

\begin{document}

\begin{rSection}{Objective}
Obtain a summer internship in 2015 of Security Engineer that can maximize my skills on reverse engineering 

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Carnegie Mellon University - Pittsburgh, PA \& Sillicon Valley, CA} \hfill {\em Dec. 2015(Expected)} \\ 
M.S. in Information Technology - Mobility, Information Networking Institute(INI) \\
{\bf\em Relevant coursework:}
\begin{inparaenum}[\itshape 1\upshape)]
\item Distributed System{\em(Fall 2014)}
\item Fundamentals of Computer Networks{\em(Fall 2014)}
\item Introduction to Information Security{\em(Fall 2014)}
\item Introduction to Computer Systems{\em(Summer 2014)}
\end{inparaenum}


{\bf Sun Yat-sen University - Guangzhou, Guangdong, China} \hfill {\em June. 2014} \\ 
B.E. in Network Engineering, 
School of Information Science and Technology \\
Overall GPA: 3.9/4.0 Ranking 1/49

\end{rSection}


%----------------------------------------------------------------------------------------
%   ACADEMIC EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Academic Experience}

\begin{rSubsection}{Organization: Guangdong Key Laboratory of Information Security}{\em Oct. 2012 - June 2014}{Research Assistant}{Guangzhou, Guangdong, China}
\item Participated in a research on software protection against reverse engineering
\item Learned many reverse engineering tools like IDA, OllyDbg, objdump and gdb and other technical skills
\item Studied many papers about reverse engineering and software protection.
\item Designed and implemented Dung and Scarab
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Project: Scarab \& Dung, a binary obfuscator and a linker}{\em May 2013 - Apr. 2014}{}{}
\item Binary obfuscator Dung weakens disassembly, static analysis and manual tracking, and incorporates a heuristic method to generate obstructive instructions with high potency
\item Assisted with implementing Scarab, an enhanced linker that provides Dung with a flexible environment to obfuscate object code
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{Company: Flamingo, Inc (Startup)}{\em Mar. 2011 - Nov. 2013}{Co-founder \& Software Engineer}{Guangzhou, Guangdong, China}
\item Led the development of games on iOS and Android with 35 employee headcounts and \$500,000 monthly revenue by the time I left
\item Led and participated in the development of many renowned games
\item Work including \textit{mobile app development, server program development, C/S network communication, cocos2d engine, web development, all learnt by myself}
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Project: Beautiful Life, an online mobile game}{\em Dec. 2011 - May 2012}{}{}
\item Designed the network communication interface and implemented it based on ASIHttpRequest to work in client part
\item Used MySQL to organize data, Memcached to cache some frequently-used data and PHP to implement server part program
\item Responsible for the server maintenance and administrative panel website development after launch
\end{rSubsection}


\end{rSection}



%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

% \begin{rSection}{Technical Strengths}

% \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
% Computer Languages & Prolog, Haskell, AWK, Erlang, Scheme, ML \\
% Protocols \& APIs & XML, JSON, SOAP, REST \\
% Databases & MySQL, PostgreSQL, Microsoft SQL \\
% Tools & SVN, Vim, Emacs
% \end{tabular}

% \end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
