%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{paralist}

\name{Yang Pan} % Your name
\address{147 N Craig St. Apt 37 \\ Pittsburgh, PA 15213} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(312)~$\cdot$~721~$\cdot$~2965 \\ pystone9205@gmail.com \\
ysite.me} % Your phone number and email

\begin{document}

\begin{rSection}{Objective}
Obtain a summer internship in 2015 of Software Engineer Intern in Back-End (35801236) or UI Application (35799849) at Apple

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Carnegie Mellon University - Pittsburgh, PA \& Sillicon Valley, CA} \hfill {\em Dec. 2015(Expected)} \\ 
M.S. in Information Technology - Mobility, Information Networking Institute(INI) 


{\bf Sun Yat-sen University - Guangzhou, Guangdong, China} \hfill {\em June. 2014} \\ 
B.E. in Network Engineering, 
School of Information Science and Technology \\
Overall GPA: 3.9/4.0 Ranking 1/49

\end{rSection}


%----------------------------------------------------------------------------------------
%   ACADEMIC EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Experience}

\begin{rSubsection}{Flamingo, Inc (Startup)}{\em Mar. 2011 - Nov. 2013}{Co-founder \& Software Engineer}{Guangzhou, Guangdong, China}
\item Led the development of games on iOS and Android with 35 employee headcounts and \$500,000 monthly revenue by the time I left
\item Led and participated in the development of many renowned games in China
\item Focused on the mobile app development and bakc-end, proficient with \textit{Foundation and UIKit framework, C, Objective-C, C++, MySQL, PHP and Java}
\end{rSubsection}

\begin{rSubsection}{Guangdong Key Laboratory of Information Security}{\em Oct. 2012 - June 2014}{Research Assistant}{Guangzhou, Guangdong, China}
\item Participated in a research on software protection against reverse engineering
\item Learned many reverse engineering tools like IDA, OllyDbg, objdump and gdb and other technical skills
\item Designed and implemented a binary obfuscator that weakens disassembly, static analysis and manual tracking, and incorporates a heuristic method to generate obstructive instructions with high potency
\end{rSubsection}


\end{rSection}

%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

\begin{rSubsection}{Bubble, a task management app in iOS}{\em Sept. 27 - Sept. 29, 2014}{}{}
\item The product of \textit{iOS App Challenge at CMU}. Available at challengepost.com/software/bubble-bhasg.
\item Distinguishing from other silimar applications in terms of the special metaphors, integration of two time management methods, as well as the intuitive interactions.
\item Designed and implemented the data center (model), responsible for managing data and providing the interface for view and controller.

\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Fanren Xiuzhen, an MMORPG mobile game in iOS}{\em March - Nov. 2013}{}{}
\item A massive multiplayer online role playing game, where players can kill monsters, upgrade equipment and fight a duel. Available in AppStore: itunes.apple.com/cn/app/fan-ren-xiu-zhen/id682389760?mt=8
\item Designed the network communication interface and implemented it based on ASIHttpRequest to work in client part and back-end program with C++ and MySQL in server
\item Implemented the UI view and controller of key modules 
\end{rSubsection}


\end{rSection}






%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

% \begin{rSection}{Technical Strengths}

% \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
% Computer Languages & Prolog, Haskell, AWK, Erlang, Scheme, ML \\
% Protocols \& APIs & XML, JSON, SOAP, REST \\
% Databases & MySQL, PostgreSQL, Microsoft SQL \\
% Tools & SVN, Vim, Emacs
% \end{tabular}

% \end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
